A pipeline to analyse time-course gene expression data

### 2020-01-15 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2019-11-19 02:22:00.

@@

\begin{tabular}{llrr}
\toprule
  & Pathway & Percentage & Adj. p-value\\
\midrule
04060 & Cytokine-cytokine receptor interaction & 34 & 0\\
04620 & Toll-like receptor signaling pathway & 40 & 0\\
04630 & Jak-STAT signaling pathway & 33 & 0\\
03050 & Proteasome & 53 & 0\\
04621 & NOD-like receptor signaling pathway & 47 & 0\\
\addlinespace
04380 & Osteoclast differentiation & 34 & 0\\
04623 & Cytosolic DNA-sensing pathway & 45 & 0\\
04210 & Apoptosis & 37 & 0\\
04622 & RIG-I-like receptor signaling pathway & 39 & 0\\
05160 & Hepatitis C & 29 & 0\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0007224 & smoothened signaling pathway & 74 & 69 & 57.82 & 0.00041 & 0.326\\
GO:0010970 & transport along microtubule & 82 & 75 & 64.07 & 0.00045 & 0.326\\
GO:0048562 & embryonic organ morphogenesis & 155 & 137 & 121.10 & 0.00067 & 0.378\\
GO:0060173 & limb development & 92 & 84 & 71.88 & 0.00067 & 0.378\\
GO:0006805 & xenobiotic metabolic process & 47 & 45 & 36.72 & 0.00089 & 0.451\\
\addlinespace
GO:0060070 & canonical Wnt signaling pathway & 152 & 134 & 118.76 & 0.00099 & 0.456\\
GO:0019395 & fatty acid oxidation & 53 & 51 & 41.41 & 0.00133 & 0.562\\
GO:0055114 & oxidation-reduction process & 533 & 458 & 416.42 & 0.00152 & 0.593\\
GO:0090596 & sensory organ morphogenesis & 134 & 118 & 104.69 & 0.00216 & 0.783\\
GO:0010811 & positive regulation of cell-substrate ad... & 77 & 70 & 60.16 & 0.00260 & 0.879\\
\addlinespace
GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.78 & 0.00293 & 0.929\\
GO:0021510 & spinal cord development & 48 & 45 & 37.50 & 0.00339 & 1.000\\
GO:0016571 & histone methylation & 74 & 67 & 57.82 & 0.00418 & 1.000\\
GO:0042738 & exogenous drug catabolic process & 22 & 22 & 17.19 & 0.00435 & 1.000\\
GO:1901381 & positive regulation of potassium ion tra... & 22 & 22 & 17.19 & 0.00435 & 1.000\\
\bottomrule
\end{tabular}

@@

## [65] rlang_0.4.1             pkgconfig_2.0.2        

>>>>

The manuscript was last compile on 2020-01-15 09:42:00.

@@

\begin{tabular}{llrr}
\toprule
  & Pathway & Percentage & Adj. p-value\\
\midrule
04060 & Cytokine-cytokine receptor interaction & 30 & 0\\
04621 & NOD-like receptor signaling pathway & 47 & 0\\
04620 & Toll-like receptor signaling pathway & 37 & 0\\
04380 & Osteoclast differentiation & 34 & 0\\
04630 & Jak-STAT signaling pathway & 29 & 0\\
\addlinespace
04210 & Apoptosis & 37 & 0\\
04623 & Cytosolic DNA-sensing pathway & 39 & 0\\
05160 & Hepatitis C & 27 & 0\\
04622 & RIG-I-like receptor signaling pathway & 35 & 0\\
05140 & Leishmaniasis & 35 & 0\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0007224 & smoothened signaling pathway & 74 & 69 & 57.81 & 0.00041 & 0.327\\
GO:0010970 & transport along microtubule & 84 & 77 & 65.62 & 0.00045 & 0.327\\
GO:0048562 & embryonic organ morphogenesis & 155 & 137 & 121.09 & 0.00066 & 0.379\\
GO:0060173 & limb development & 92 & 84 & 71.87 & 0.00067 & 0.379\\
GO:0006805 & xenobiotic metabolic process & 47 & 45 & 36.72 & 0.00088 & 0.448\\
\addlinespace
GO:0060070 & canonical Wnt signaling pathway & 152 & 134 & 118.75 & 0.00098 & 0.454\\
GO:0019395 & fatty acid oxidation & 53 & 51 & 41.41 & 0.00133 & 0.564\\
GO:0055114 & oxidation-reduction process & 533 & 458 & 416.40 & 0.00151 & 0.591\\
GO:0090596 & sensory organ morphogenesis & 134 & 118 & 104.68 & 0.00215 & 0.782\\
GO:0010811 & positive regulation of cell-substrate ad... & 77 & 70 & 60.15 & 0.00259 & 0.824\\
\addlinespace
GO:0016571 & histone methylation & 77 & 70 & 60.15 & 0.00259 & 0.824\\
GO:0021510 & spinal cord development & 49 & 46 & 38.28 & 0.00280 & 0.829\\
GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.78 & 0.00293 & 0.829\\
GO:0060078 & regulation of postsynaptic membrane pote... & 68 & 62 & 53.12 & 0.00384 & 1.000\\
GO:0031109 & microtubule polymerization or depolymeri... & 61 & 56 & 47.65 & 0.00405 & 1.000\\
\bottomrule
\end{tabular}

@@

## [65] rlang_0.4.2             pkgconfig_2.0.2        
